### 2022-04-07 paper/theorems/main.tex

\chapter{Теоремы}
\subfile{theorems/chisq-laplace}
%
\subfile{theorems/laplace-var-change}
%
\subfile{theorems/product-series}
%
\subfile{theorems/laurent-1}
%
\subfile{theorems/laurent-2}
%
\subfile{theorems/laurent-3}
%
\subfile{theorems/modified-jordan.tex}